Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-09-01 Docs/Paper/LaTex/template.tex
rename ESBMC solution in Table 2

%----------------------------------------------
\subsection{Multi-core ESBMC with OpenMP using Workers}
\label{Multi-core-ESBMC-with-OpenMP-using-workers}
%----------------------------------------------

@@

%----------------------------------------------
\subsection{Multi-core ESBMC with OpenMP using Binary Search}
\label{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}
%----------------------------------------------

@@

%MultiCore ESBMC
\multirow{2}{*}{\textbf{ESBMC Multicore}}
&  T(s)   &  2   &  6   &  7   &  1615   &  TO    &  TO   &  TO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
\hline

%ESBMC Parallel sequential
\multirow{2}{*}{\textbf{ESBMC Parallel Sequential}}
&  T(s) &  4 &  10   &  11   &  2238   &  TO    &  MO   &  MO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
\hline

%ESBMC Parallel Binary
\multirow{2}{*}{\textbf{ESBMC Parallel Binary}}
&  T(s)   &  6   &  5   &  6   &  207   &  TO    &  MO   &  MO \\
&  Hp   &  15   &  47   &  38   &  241   &  -    &  -   &  -  \\
\bottomrule[1.5pt]
\end{tabular}
\label{Experimental-results-of-the-complex-benchmarks}
\end{table*}

>>>>

%----------------------------------------------
\subsection{Multi-core ESBMC with OpenMP using Workers (ESBMC-PS)}
\label{Multi-core-ESBMC-with-OpenMP-using-workers}
%----------------------------------------------

@@

%----------------------------------------------
\subsection{Multi-core ESBMC with OpenMP using Binary Search (ESBMC-PB)}
\label{Multi-core-ESBMC-with-OpenMP-using-Binary-Search}
%----------------------------------------------

@@

%MultiCore ESBMC
\multirow{2}{*}{\textbf{ESBMC-MC}}
&  T(s)   &  2   &  6   &  7   &  1615   &  TO    &  TO   &  TO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
\hline

%ESBMC Parallel sequential
\multirow{2}{*}{\textbf{ESBMC-PS}}
&  T(s) &  4 &  10   &  11   &  2238   &  TO    &  MO   &  MO  \\
&  Hp   &  15   &  47   &  31   &  241   &  -    &  -   &  -  \\
\hline

%ESBMC Parallel Binary
\multirow{2}{*}{\textbf{ESBMC-PB}}
&  T(s)   &  6   &  5   &  6   &  207   &  TO    &  MO   &  MO \\
&  Hp   &  15   &  47   &  38   &  241   &  -    &  -   &  -  \\
\bottomrule[1.5pt]
\end{tabular}
\label{Experimental-results-of-the-complex-benchmarks}
\end{table*}
